Supplementary Information

### 2020-11-21 doc/manuscript/MEE_manuscript_SI.Rmd
fix SC elevation
#92

\newpage
## `r site_details_legend` 
```{r eval = TRUE, echo=FALSE, warning=FALSE}
library(knitr)
library(kableExtra)
S1 <- read.csv("tables_figures/site_details.csv", stringsAsFactors = FALSE, check.names = FALSE)
kable(S1, format = "latex", booktabs = TRUE,   escape = F)%>%
  column_spec(2, width = "3cm") %>%
  column_spec(5, width = "2cm") %>%
  column_spec(6, width = "2cm") %>%
  column_spec(7, width = "1.5cm") %>%
  kable_styling(latex_options = c("scale_down", "hold_position"), protect_latex = T) 
```

>>>>

\newpage
## `r site_details_legend` 
```{r eval = TRUE, echo=FALSE, warning=FALSE}
library(knitr)
library(kableExtra)
S1 <- read.csv("tables_figures/site_details.csv", stringsAsFactors = FALSE, check.names = FALSE)
kable(S1, format = "latex", booktabs = TRUE,   escape = F)%>%
  column_spec(2, width = "3cm") %>%
  column_spec(5, width = "2cm") %>%
  column_spec(6, width = "2cm") %>%
  column_spec(7, width = "1.5cm") %>%
  kable_styling(latex_options = c("scale_down", "hold_position"), protect_latex = T) 
```
* Refers to approximate period during which woody growth ceases (dry season in the tropics, winter for temperate and boreal sites).
